\section{References}
\small
\begin{multicols}{2}
\begin{thebibliography}{99}
\bibitem{russell2016artificial} Russell, S., \& Norvig, P. (2016). \textit{Artificial Intelligence: A Modern Approach} (3rd ed.). Pearson.
\bibitem{mcconnell2004code} McConnell, S. (2004). \textit{Code Complete} (2nd ed.). Microsoft Press.
\bibitem{fowler2006continuous} Fowler, M. (2006). \textit{Continuous Delivery: Reliable Software Releases through Build, Test, and Deployment Automation}. Addison-Wesley.
\bibitem{kim2016devops} Kim, G., Behr, K., \& Spafford, D. (2016). \textit{The DevOps Handbook: How to Create World-Class Agility, Reliability, \& Security in Technology Organizations}. IT Revolution Press.
\bibitem{martin2017clean} Martin, R. C. (2017). \textit{Clean Architecture: A Craftsman's Guide to Software Structure and Design}. Prentice Hall.
\bibitem{larman2004applying} Larman, C. (2004). \textit{Applying UML and Patterns: An Introduction to Object-Oriented Analysis and Design and Iterative Development} (3rd ed.). Prentice Hall.
\bibitem{poppendieck2003lean} Poppendieck, M., \& Poppendieck, T. (2003). \textit{Lean Software Development: An Agile Toolkit}. Addison-Wesley.
\bibitem{shostack2014threat} Shostack, A. (2014). \textit{Threat Modeling: Designing for Security}. Wiley.
\bibitem{roberts2015scaling} Roberts, M. (2015). \textit{Scaling Teams: Strategies for Building Successful Teams}. O'Reilly Media.
\bibitem{harris2016backup} Harris, S. (2016). \textit{Backup \& Recovery: Inexpensive Backup Solutions for Open Systems}. O'Reilly Media.
\bibitem{sommerville2011software} Sommerville, I. (2011). \textit{Software Engineering} (9th ed.). Addison-Wesley.
\bibitem{zhao2018progressive} Zhao, X. (2018). \textit{Progressive Web Applications: Enhancing the Web Experience}. Springer.
\bibitem{jamstack2020} Jamstack. (2020). \textit{The Jamstack Architecture: Decoupling the Front-End and Back-End}. O'Reilly Media.
\bibitem{wasm2019} WebAssembly Community Group. (2019). \textit{WebAssembly: High-Performance Code on the Web}. W3C.
\bibitem{miller2021ai} Miller, A. (2021). \textit{AI-Powered Development Tools: Accelerating Coding and Testing}. Wiley.
\bibitem{nielsen2022nlp} Nielsen, J. (2022). \textit{Natural Language Processing in Web Development}. MIT Press.
\bibitem{jones2023personalization} Jones, R. (2023). \textit{Personalized Web Experiences: Leveraging AI for Better User Interaction}. Cambridge University Press.
\bibitem{li2021cybersecurity} Li, S. (2021). \textit{AI in Cybersecurity: Enhancing Threat Detection and Response}. Elsevier.
\bibitem{smith2020microservices} Smith, J. (2020). \textit{Microservices Architecture for Modern Web Applications}. Packt Publishing.
\bibitem{johnson2021cloud} Johnson, L. (2021). \textit{Cloud Computing and DevOps: Bridging the Gap}. CRC Press.
\bibitem{martin2022devops} Martin, P. (2022). \textit{DevOps Practices: Automation and CI/CD}. O'Reilly Media.
\bibitem{brown2023iac} Brown, K. (2023). \textit{Infrastructure as Code: Managing Your Cloud Infrastructure}. Apress.
\bibitem{adams2021zerotrust} Adams, R. (2021). \textit{Zero Trust Architecture: Security for Modern Applications}. Springer.
\bibitem{lee2022security} Lee, H. (2022). \textit{Modern Security Practices in Web Development}. Wiley.
\bibitem{kim2021encryption} Kim, T. (2021). \textit{End-to-End Encryption: Protecting Data in Transit}. MIT Press.
\bibitem{garcia2023secure} Garcia, M. (2023). \textit{Secure Coding Practices: Ensuring Application Security}. Springer.
\bibitem{wang2021testing} Wang, J. (2021). \textit{Automated Security Testing in CI/CD Pipelines}. Elsevier.
\bibitem{miller2022quantum} Miller, A. (2022). \textit{Quantum Computing and Its Implications for Web Development}. CRC Press.
\bibitem{doe2023fiveg} Doe, J. (2023). \textit{5G Technology and Its Impact on Web Performance}. Wiley.
\bibitem{white2021web3} White, E. (2021). \textit{Web 3.0: The Decentralized Web and Blockchain Technology}. MIT Press.
\end{thebibliography}
\end{multicols}
